### 2019-12-24 survival.tex
revised assignments

\section{Survival Analysis}
\label{sec:survival}
\fix{George's survival analysis}

@@

The Cox proportional hazards (CPH) regression analys takes the hazard function above and a set of covariates $x$ and models $k$s GPU hazard as
\begin{displaymath}
  H_k(t) = H_0(t)e^{\sum\limits_{i=1}^n{\beta x}}
\end{displaymath}
That is, a base hazard rate multiplied by a function of
covariates. The key assumption in the CPH model is that the "hazards"
are multipliers on the "baseline hazard" but the estimate of the
baseline hazard is nonparametric, meaning it makes no specific
distributional assumption and just learns from the data (unlike
analyses that assume for example a Weibul or an exponential
model). The multiplicative assumption is that the hazard curves do not
cross and are multiples of each other. The multiplier is the *hazard
coefficient*. For example, if the baseline is *node0* and the *node2*
hazard is 2, then *node2* sees twice as many failures as *node0* on
average.

>>>>

\section{Survival Analysis}
\label{sec:survival}
\fix{George's survival analysis, check \protect\pkg{finalfit}}

@@

The Cox proportional hazards (CPH) regression analys \cite{Cox1972,Harrell2015} takes the hazard function above and a set of covariates $x$ and models $k$s GPU hazard as
\begin{displaymath}
  H_k(t) = H_0(t)e^{\sum\limits_{i=1}^n{\beta x}}
\end{displaymath}
That is, a base hazard rate multiplied by a function of
covariates. The key assumption in the CPH model is that the "hazards"
are multipliers on the "baseline hazard" but the estimate of the
baseline hazard is nonparametric, meaning it makes no specific
distributional assumption and just learns from the data (unlike
analyses that assume for example a Weibul or an exponential
model). The multiplicative assumption is that the hazard curves do not
cross and are multiples of each other. The multiplier is the *hazard
coefficient*. For example, if the baseline is *node0* and the *node2*
hazard is 2, then *node2* sees twice as many failures as *node0* on
average.
